% !TeX encoding = UTF-8
% !TeX spellcheck = en_GB
\documentclass[a4paper, 11pt]{article}
%\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}

%margin
\usepackage[margin=2cm]{geometry}
%\usepackage[margin=1in]{geometry}
\usepackage{changepage}
%line spacing
\renewcommand{\baselinestretch}{1.15}
%\renewcommand{\baselinestretch}{1.6}
%lists
\usepackage{enumitem}
%multi-columns
\usepackage{multicol}
%encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%English
\usepackage[english]{babel}
%colors
\usepackage[dvipsnames,svgnames,table]{xcolor}
%tables
\usepackage{multirow}
\usepackage{longtable}
\usepackage{tabularx}
%for math
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{mathdots}
\usepackage{nicefrac}
\usepackage{stmaryrd}
\usepackage{makecell}
%for images
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\graphicspath{{./img/}{./plots/}{./crossings/}}
%for plots
\usepackage{tikz}
\usepackage{adjustbox}
%links
%\usepackage[hyphens]{url}
\usepackage{hyperref}
%\hypersetup{colorlinks=true}
%citations
\bibliographystyle{unsrtnat}
%code
\usepackage{minted}
%\usepackage[cache=false]{minted}
%\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\definecolor{CodeColor}{RGB}{100, 100, 100}


%environments
\newtheorem*{notation}{Notation}
\newtheorem{definition}{Definition}[section]
\newtheorem*{claim}{Claim}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{property}{Property}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[section]
\newtheorem*{conjecture}{Conjecture}
%commands
%\newcommand{\name}[num]{definition}
\newcommand{\primes}{\mathbb{P}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\D}{\mathbb{D}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\halfplane}{\mathbb{H}}
%\newcommand{\dim}[1]{\text{dim}(#1)}
\newcommand{\SL}[2]{\text{SL}_{#1}(#2)}
\newcommand{\Norm}[2][]{\text{Norm}_{#1}(#2)}
\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\abs}[1]{| #1 |}
\newcommand{\curt}[1]{\sqrt[3]{#1}}
\newcommand{\Ker}[1]{\text{Ker}(#1)}
\newcommand{\Image}[1]{\text{Im}(#1)}
\newcommand{\Gal}[1]{\text{Gal}(#1)}
\newcommand{\Frob}[2]{\text{Frob}_{#1}(#2)}
\newcommand{\Tr}[1]{\text{Tr}(#1)}
\newcommand{\Det}[1]{\text{Det}(#1)}
\newcommand{\End}[1]{\text{End}(#1)}
\newcommand{\Aut}[1]{\text{Aut}(#1)}
\newcommand{\legendre}[2]{\left( \frac{#1}{#2} \right)}
\newcommand{\degree}[1]{\partial #1}
\newcommand{\diam}[1]{\text{diam}(#1)}




\begin{document}
	\include{title_page}
	\footnotetext{Title inspired of the pseudo-joke "Why did the chicken cross the road?" (see \url{https://en.wikipedia.org/wiki/Why_did_the_chicken_cross_the_road\%3F}).}
	\begin{center}
		\LARGE Percolation Fractals
	\end{center}
	\vspace{0.5cm}
	\begin{abstract}
		Percolations are geometric figures obtained after repetitively removing some material from an initial set, in our case, a cuboid.
		Studying their properties provide a better understanding of some physical models for materials: some porous materials are modelled using percolations.
		In this paper, we study mathematical properties of percolations starting with cuboids of any dimensions, and make numerical experiments on the two and three dimensional cases.
		
		We will introduce the concept of dimensionality for sets, and the concept of fractal.
		We will then narrow down our interest to a special type of fractals: the one obtained by percolation.
		Two competing models will be studied: the classical percolation, and the recursive scheme.
		
		After discussing some basic properties (density, dimension, size of the central "blob"), we will look at crossings on percolations.
		This is the main purpose of this paper, we will derive some mathematical result in extreme cases, and use some innovative algorithms to obtain relevant numerics.
		Finally, we will extend techniques used in previous literature for percolations in two dimensions to acquire knowledge in more general settings. 
	\end{abstract}
	
	\vspace{2.5cm}
	\begin{center}
		\textbf{Acknowledgment}
	\end{center}
	{
		\small
		\hspace{1cm}
		First of all, I would like to thank my supervisor, Ben Hambly, for guiding and supporting through this project.
		I would like to thank the whole administrative team of Oxford, for all the help they provided despite the pandemic context.
	}

	\vspace{2.5cm}
	\begin{center}
		\textbf{Word Count}
	\end{center}
	\begin{center}
		%\textit{Word count by Overleaf}
		\begin{tabular}{r l}
			Total Words: & 7432 \\
			Headers: & 87 \\
			Math Inline: & 618 \\
			Math Display: & 29 \\
			Figures: & 38 \\
			Algorithms: & 2 \\
		\end{tabular}
	\end{center}
	
	\newpage
	
	\tableofcontents
	
	\include{Introduction}
	\include{BackgroundTheory}
	\include{PercolationFractals}
	\include{PercolationCrossings}
	%\include{PercolationProjections}
	\include{Conclusion}
	
	\bibliography{references}
	
	\appendix
	\include{title_appendix}
	\include{FractalsAddon}
	\include{CrossingAlgorithms}
	
\end{document}
